FinalManuscript_DISCS_UG

### 2018-07-16 parts/01_introduction_01contextofstudy.tex

Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys, using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel. Much research has been done on the development and application of various cryptosystems.

>>>>

Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel. Much research has been done on the development and application of various cryptosystems.

### 2018-07-16 parts/02_relatedliterature_02commonimageprocessingoperations.tex

\begin{figure*}[!ht]
    \centering
    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/SpatialFilter.png}
    \caption{(a) A sample image $R$. (b) A sample kernel $k$.}
    \label{fig:spatialfilter}
\end{figure*}
For example, using the image and kernel given in Figure \ref{fig:spatialfilter}, we can calculate the value in the third row and fourth column of the resulting image $R^\prime$ as follows:
\begin{align*}
	R^\prime(3,4) &= \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(3+s,4+t)}}\\
	&= (0.0625\times 200) + (0.1250\times 249) + (0.0625\times 255) \\
	&+ (0.1250\times 143) + (0.2500\times 223) + (0.1250\times 255) \\
	&+ (0.0625\times 196) + (0.1250\times 236) + (0.0625\times 255)\\
	&= 223.
\end{align*}
Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosytems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved. This was performed in the implementation of spatial filters in the \textit{CryptoImg} library~\cite{ziad_cryptoimg:_2016}. We wish to implement spatial filters using a similar approach, and assess how preserving spatial correlation between pixels can impact the security of the encrypted image.

\subsection{Common Spatial Filtering Kernels}
Edge detection is used to find and determine the boundaries in an image, commonly used in applications such as image segmentation and feature extraction. This works by detecting so-called \textit{edges}, areas that have abrupt changes in intensity.
One common method of performing edge detection is the Sobel operator, which uses two spatial filters to approximate the gradient in an image. Given an image $R$, and the kernels
\begin{equation}
    g_x =
    \begin{bmatrix}
        -1 & 0 & 1 \\
        -2 & 0 & 2 \\
        -1 & 0 & 1
    \end{bmatrix}
    \qquad\text{and}\qquad
    g_y =
    \begin{bmatrix}
        1 & 2 & 1 \\
        0 & 0 & 0 \\
        -1 & -2 & -1
    \end{bmatrix},
\end{equation}
$g_x \ast R$ yields the horizontal component of the gradient, while $g_y \ast R$ yields the vertical component of the gradient.

>>>>

\begin{figure*}[!ht]
    \centering
    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/SpatialFilter.png}
    \caption{A sample image $R$ and sample kernel $k$.}
    \label{fig:spatialfilter}
\end{figure*}
For example, using the image and $3 \times 3$ kernel given in Figure \ref{fig:spatialfilter}, we can calculate the value in the third row and fourth column of the resulting image $R^\prime$ by adding the products of entries in $k$ with the corresponding entries in $R$, found in an $3 \times 3$ region around $R(3,4)$.
\begin{align*}
	R^\prime(3,4) &= \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(3+s,4+t)}}\\
	&= (0.0625\times 200) + (0.1250\times 249) + (0.0625\times 255) \\
	&+ (0.1250\times 143) + (0.2500\times 223) + (0.1250\times 255) \\
	&+ (0.0625\times 196) + (0.1250\times 236) + (0.0625\times 255)\\
	&= 223.
\end{align*}
Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosytems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved. This was performed in the implementation of spatial filters in the \textit{CryptoImg} library~\cite{ziad_cryptoimg:_2016}. We wish to implement spatial filters using a similar approach, and assess how preserving spatial correlation between pixels can impact the security of the encrypted image.

\subsection{Common Spatial Filtering Kernels}
Edge detection is used to find and determine the boundaries in an image, commonly used in applications such as image segmentation and feature extraction. This works by detecting so-called \textit{edges}, areas that have abrupt changes in intensity.
One common method of performing edge detection is the Sobel operator, which uses two spatial filters to approximate the gradient of an image. Given an image $R$, and the kernels
\begin{equation}
    g_x =
    \begin{bmatrix}
        -1 & 0 & 1 \\
        -2 & 0 & 2 \\
        -1 & 0 & 1
    \end{bmatrix}
    \qquad\text{and}\qquad
    g_y =
    \begin{bmatrix}
        1 & 2 & 1 \\
        0 & 0 & 0 \\
        -1 & -2 & -1
    \end{bmatrix},
\end{equation}
$g_x \ast R$ yields the horizontal component of the gradient, while $g_y \ast R$ yields the vertical component of the gradient.
